OG-Analysis

### 2019-09-15 OG-Analysis_GD.Rmd
took out _freq naming

##Frequency of Gamma Deltas to start with
```{r}
pvals_gd(subset(CD3, CD3$Stim=="UN"), "GD_freq")
plot_with_all_stats(subset(CD3, CD3$Stim=="UN"), "GD_freq")
plot_3(subset(CD3, CD3$Stim=="UN"), "GD_freq")
pvals_gd(subset(CD3, CD3$Stim=="SWAP"), "GD_freq")
```

##Proliferation of Gamma Deltas
###Including cd4/cd8
```{r gd}
DF<-subset(gd, gd$Stim=="SWAP")
plot_with_all_stats(DF, "OG_freq")
plot_3(DF,  "OG_freq")
ggplot(DF, aes(x=SM, y=OG_freq, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

###Excluding CD4/CD8
```{r GD}
DF<-subset(GD, GD$Stim=="SWAP")
plot_with_all_stats(DF, "OG_freq")
plot_3(DF,  "OG_freq")
ggplot(DF, aes(x=SM, y=OG_freq, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

##Are starting Frequencies related to expansion
```{r}
start<-select(CD3, Sample, Stim, Donor, GD_freq)
middle1<-filter(start, Stim=="UN")
middle2<-filter(start, Stim=="SWAP")
end<-select(gd, Sample, Stim, TB, SM, Donor, OG_freq)%>%filter(Stim=="SWAP")

test<-merge(middle1, middle2, by=c("Donor"))
test2<-merge(test, end, by="Donor")
melt<-melt(test2, id.vars=c("Donor", "TB", "SM"), measure.vars=c("GD_freq.x", "GD_freq.y"))
ggplot(melt, aes(x=variable, y=value, color=TB))+geom_point()+geom_line(aes(group=Donor))+facet_grid(~TB)+scale_x_discrete(labels=c("Starting freq", "Swap Freq", "Proliferating Freq"))

test2$ratio<-test2$GD_freq.y/test2$GD_freq.x
plot_with_all_stats(test2, "ratio")+labs(title="Expansion of gd")
plot_3(test2, "ratio")+labs(title="Expansion of gd")

test2$dif<-test2$GD_freq.y-test2$GD_freq.x
plot_with_all_stats(test2, "dif")+labs(title="Expansion of gd")
plot_3(test2, "dif")+labs(title="Expansion of gd")
```

@@

phenotype$include<-1
for(i in 1:length(phenotype$include)){
    if(is.na(phenotype$OG_freq[i])){
        phenotype$include[i]<-0
    }
}
kable(xtabs(~include+SM+TB, phenotype[phenotype$Stim=="SWAP",]))
x<-split(phenotype[phenotype$Stim=="SWAP",], list(phenotype$SM, phenotype$TB))
lapply(x, function(g) table(g$include))

@@

phenotype$include<-1
for(i in 1:length(phenotype$include)){
    if(is.na(phenotype$OG_freq[i])){
        phenotype$include[i]<-0
    }
}
kable(xtabs(~include+SM+TB, phenotype[phenotype$Stim=="SWAP",]))
x<-split(phenotype[phenotype$Stim=="SWAP",], list(phenotype$SM, phenotype$TB))
kable(sapply(x, function(g) table(g$include)))
```

##gd
```{r gd og SWAP}
library(dplyr)
library(knitr)
DF<-subset(OG_gd, OG_gd$Stim=="SWAP")
#split by both TB and SM so you have a list of 6 data frames- each of which is a group of interest
x<-split(DF, list(DF$TB, DF$SM))
#for each dataframe in the list, return the column names of the columns where the sum of the number of rows that do not have missing data is more than 0. It's a weird double negative. But basically makes a list of the columns that have sufficient data.
y<-lapply(x, function(g) names(g[, colSums(!is.na(g)) > 0]))
#each entry in the list has to be extracted and named
a<-unlist(y[1])
b<-unlist(y[2])
c<-unlist(y[3])
d<-unlist(y[4])
#then find the intersection of all the lists. Aka which column names have sufficient data in all 4 TB-SM groups
test<-Reduce(intersect, list(a,b,c,d))
#this will also include metadata so we remove those column names and can phenotype using the standard pvals function from the beginning
colnames<-c(test[1:39], test[45:56])
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

```{r}
test<-filter(DF, !is.na(OG_freq))
kable(xtabs(~TB+SM, test))
```

@@

plot_with_all_stats(DF, "IL4_freq")

plot_3(DF, "IL4_freq")
plot_3(DF, "TNFa_freq")
plot_3(DF, "IFNg_freq")

ggplot(DF, aes(x=SM, y=IL4_freq, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()

ggplot(DF, aes(x=SM, y=TNFa_freq, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()

ggplot(DF, aes(x=SM, y=IFNg_freq, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()
```

@@

formula<-y~x
DF<-merge(select(PBMC, Donor, SchistosomaIntensity), CD3[CD3$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=OG_freq, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="CD3")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), CD3_OG[CD3_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=GD_freq, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="CD3")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD[GD$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=OG_freq, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="GD")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD_OG[GD_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=IL4_freq, y=SchistosomaIntensity, color=TB))+
    geom_point()+
    scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))+
    stat_smooth(method="lm", formula = formula)+
    stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.15,
               formula = formula, parse = TRUE, size = 3)

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD_OG[GD_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=TNFa_freq, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="GD")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD_OG[GD_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=IFNg_freq, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="GD")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

@@

##GD
```{r GD og swap}
library(dplyr)
library(knitr)
DF<-subset(OG_GD, OG_GD$Stim=="SWAP")
#split by both TB and SM so you have a list of 6 data frames- each of which is a group of interest
x<-split(DF, list(DF$TB, DF$SM))
#for each dataframe in the list, return the column names of the columns where the sum of the number of rows that do not have missing data is more than 0. It's a weird double negative. But basically makes a list of the columns that have sufficient data.
y<-lapply(x, function(g) names(g[, colSums(!is.na(g)) > 0]))
#each entry in the list has to be extracted and named
a<-unlist(y[1])
b<-unlist(y[2])
c<-unlist(y[3])
d<-unlist(y[4])
#then find the intersection of all the lists. Aka which column names have sufficient data in all 4 TB-SM groups
test<-Reduce(intersect, list(a,b,c,d))
#this will also include metadata so we remove those column names and can phenotype using the standard pvals function from the beginning
colnames<-c(test[1:32], test[38:49])
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

```{r}
test<-filter(DF, !is.na(OG_freq))
kable(xtabs(~TB+SM, test))
```

>>>>

##Checking if I can combine SM- and SM+ in TB groups
###CD3 T cells
```{r}
DF<-subset(CD3, CD3$Stim=="SWAP")
colnames<-c("GD","OG")
for(col in colnames){
    y<-pvals_SM(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}

DF<-subset(CD3_OG, CD3_OG$Stim=="SWAP")
colnames<-c("GD")
for(col in colnames){
    y<-pvals_SM(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}

```
###total gamma delta
```{r}
DF<-subset(gd, gd$Stim=="SWAP")
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_SM(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}

###proliferating gamma deltas
```{r}
DF<-subset(gd_OG, gd_OG$Stim=="SWAP")
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_SM(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

##Frequency of Gamma Deltas to start with
```{r}
pvals_gd(subset(CD3, CD3$Stim=="UN"), "GD")
plot_with_all_stats(subset(CD3, CD3$Stim=="UN"), "GD")
plot_3(subset(CD3, CD3$Stim=="UN"), "GD")
pvals_gd(subset(CD3, CD3$Stim=="SWAP"), "GD")
```

##Proliferation of Gamma Deltas
###Including cd4/cd8
```{r gd}
DF<-subset(gd, gd$Stim=="SWAP")
DF$SM<-factor(DF$SM, levels=c("X", "SM"))
plot_with_all_stats(DF, "OG")
plot_3(DF,  "OG")
ggplot(DF, aes(x=SM, y=OG, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means(label.y=85, label.x=1.3)+scale_x_discrete(labels=c("SM-", "SM+"))
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

###Excluding CD4/CD8
```{r GD}
DF<-subset(GD, GD$Stim=="SWAP")
plot_with_all_stats(DF, "OG")
plot_3(DF,  "OG")
ggplot(DF, aes(x=SM, y=OG, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

##Are starting Frequencies related to expansion
```{r}
start<-select(CD3, Sample, Stim, Donor, GD)
middle1<-filter(start, Stim=="UN")
middle2<-filter(start, Stim=="SWAP")
end<-select(gd, Sample, Stim, TB, SM, Donor, OG)%>%filter(Stim=="SWAP")

test<-merge(middle1, middle2, by=c("Donor"))
test2<-merge(test, end, by="Donor")
melt<-melt(test2, id.vars=c("Donor", "TB", "SM"), measure.vars=c("GD.x", "GD.y"))
ggplot(melt, aes(x=variable, y=value, color=TB))+geom_point()+geom_line(aes(group=Donor))+facet_grid(~TB)+scale_x_discrete(labels=c("Starting freq", "Swap Freq", "Proliferating Freq"))

test2$ratio<-test2$GD.y/test2$GD.x
plot_with_all_stats(test2, "ratio")+labs(title="Expansion of gd")
plot_3(test2, "ratio")+labs(title="Expansion of gd")

test2$dif<-test2$GD.y-test2$GD.x
plot_with_all_stats(test2, "dif")+labs(title="Expansion of gd")
plot_3(test2, "dif")+labs(title="Expansion of gd")
```

@@

phenotype$include<-1
for(i in 1:length(phenotype$include)){
    if(is.na(phenotype$OG[i])){
        phenotype$include[i]<-0
    }
}
kable(xtabs(~include+SM+TB, phenotype[phenotype$Stim=="SWAP",]))
x<-split(phenotype[phenotype$Stim=="SWAP",], list(phenotype$SM, phenotype$TB))
lapply(x, function(g) table(g$include))

@@

phenotype$include<-1
for(i in 1:length(phenotype$include)){
    if(is.na(phenotype$OG[i])){
        phenotype$include[i]<-0
    }
}
kable(xtabs(~include+SM+TB, phenotype[phenotype$Stim=="SWAP",]))
x<-split(phenotype[phenotype$Stim=="SWAP",], list(phenotype$SM, phenotype$TB))
kable(sapply(x, function(g) table(g$include)))
```

##gd
```{r gd og SWAP}
library(dplyr)
library(knitr)
DF<-subset(OG_gd, OG_gd$Stim=="SWAP")
#split by both TB and SM so you have a list of 6 data frames- each of which is a group of interest
x<-split(DF, list(DF$TB, DF$SM))
#for each dataframe in the list, return the column names of the columns where the sum of the number of rows that do not have missing data is more than 0. It's a weird double negative. But basically makes a list of the columns that have sufficient data.
y<-lapply(x, function(g) names(g[, colSums(!is.na(g)) > 0]))
#each entry in the list has to be extracted and named
a<-unlist(y[1])
b<-unlist(y[2])
c<-unlist(y[3])
d<-unlist(y[4])
#then find the intersection of all the lists. Aka which column names have sufficient data in all 4 TB-SM groups
test<-Reduce(intersect, list(a,b,c,d))
#this will also include metadata so we remove those column names and can phenotype using the standard pvals function from the beginning
colnames<-c(test[1:39], test[45:52])
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

```{r}
test<-filter(DF, !is.na(OG))
kable(xtabs(~TB+SM, test))
```

@@

plot_with_all_stats(DF, "IL4")

plot_3(DF, "IL4")
plot_3(DF, "TNFa")
plot_3(DF, "IFNg")

ggplot(DF, aes(x=SM, y=IL4, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()

ggplot(DF, aes(x=SM, y=TNFa, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()

ggplot(DF, aes(x=SM, y=IFNg, fill=SM))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=.1)+stat_compare_means()
```

@@

formula<-y~x
DF<-merge(select(PBMC, Donor, SchistosomaIntensity), CD3[CD3$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=OG, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="CD3")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), CD3_OG[CD3_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=GD, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="CD3")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD[GD$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=OG, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="GD")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD_OG[GD_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=IL4, y=SchistosomaIntensity, color=TB))+
    geom_point()+
    scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))+
    stat_smooth(method="lm", formula = formula)+
    stat_poly_eq(aes(label = paste(..rr.label..)), 
               label.x.npc = "right", label.y.npc = 0.15,
               formula = formula, parse = TRUE, size = 3)

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD_OG[GD_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=TNFa, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="GD")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

DF<-merge(select(PBMC, Donor, SchistosomaIntensity), GD_OG[GD_OG$Stim=="SWAP",], by="Donor")
ggplot(DF[DF$SM=="SM",], aes(x=IFNg, y=SchistosomaIntensity, color=TB))+geom_point()+stat_smooth(method="lm")+labs(title="GD")+scale_color_manual(values =c("#00AFBB", "#E7B800", "#FC4E07"))

@@

##GD
```{r GD og swap}
library(dplyr)
library(knitr)
DF<-subset(OG_GD, OG_GD$Stim=="SWAP")
#split by both TB and SM so you have a list of 6 data frames- each of which is a group of interest
x<-split(DF, list(DF$TB, DF$SM))
#for each dataframe in the list, return the column names of the columns where the sum of the number of rows that do not have missing data is more than 0. It's a weird double negative. But basically makes a list of the columns that have sufficient data.
y<-lapply(x, function(g) names(g[, colSums(!is.na(g)) > 0]))
#each entry in the list has to be extracted and named
a<-unlist(y[1])
b<-unlist(y[2])
c<-unlist(y[3])
d<-unlist(y[4])
#then find the intersection of all the lists. Aka which column names have sufficient data in all 4 TB-SM groups
test<-Reduce(intersect, list(a,b,c,d))
#this will also include metadata so we remove those column names and can phenotype using the standard pvals function from the beginning
colnames<-c(test[1:32])
for(col in colnames){
    y<-pvals_collapse(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

```{r}
test<-filter(DF, !is.na(OG))
kable(xtabs(~TB+SM, test))
```
